En garde! Unguarded iteration for reversible computation in the Delay monad\thanks{Supported by organization x.}

### 2019-04-29 mpc19/paper.tex
Added section on semantcis

% Semantics
\newcommand{\semTy}[1]{{\llbracket #1 \rrbracket}_\mathsf{Ty}}
\newcommand{\semMu}[1]{{\llbracket #1 \rrbracket}_\mu}
\newcommand{\semTm}[1]{{\llbracket #1 \rrbracket}_\lr}

@@

@@

Terms of \Pio\ are modelled as morphism of $\Inv\Dapprox$,
i.e. partial isomorphisms. Formally, we define an operation:
\[
\semTm - : (A \lr B) \to 
\]

>>>>

% Semantics
\newcommand{\semTy}[1]{{\llbracket #1 \rrbracket}_\mathsf{Ty}}
\newcommand{\semMu}[1]{{\llbracket #1 \rrbracket}_\mu}
\newcommand{\semTm}[1]{{\llbracket #1 \rrbracket}_{\lr}}
\newcommand{\semEq}[1]{{\llbracket #1 \rrbracket}_{\LR}}

@@

Summing up, in this section we have showed that the $\traceD$ operator
can be restricted to act on partial isomorphisms. That is, the
following type is inhabited:
\[
\mathsf{semTrace} : A + C\simeq B + C \to A \simeq C
\]

@@

Terms of \Pio\ are modelled as morphism of $\Inv\Dapprox$,
i.e. partial isomorphisms. Formally, we define an operation:
\[
\semTm - : (A \lr B) \to \semTy A \, \rho \simeq \semTy B \, \rho
\]
We refer the interested reader to our Agda formalization for a
complete definition of the interpretation of terms. We only emphasize
the semantics of the trace operator: $\semTm {\trace\,f} =
\mathsf{semTrace}\,\semTm f$.

Term equivalences of \Pio\ are modelled as morphism equalities in
$\Inv\Dapprox$, i.e. proofs of weak bisimilarity between two
morpshisms. Formally, we define an operation:
\[
\semEq - : (f \LR g) \to \semTm f \approx \semTm g
\]
Again we refer the interested reader to our Agda formalization for a
complete definition of the interpretation of term equivalences.
